Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-10-20 paper/main.tex
formatting

We will go into the details of the model for rod-shaped bacteria.
The mechanical behaviour of rod-shaped bacteria is governed by a plethora of effects.
In this work, we aim to establish a model which is abstract enough such that it can be reused for
many types of rod-shaped bacteria but also explicit enough such that we can quantify its parameters.
We are thus aiming to work with a minimal set of assumptions that is as general as possible but
still specific to rod-shaped bacteria.

Given this delicate balance, it is evident that numerous cellular processes will be excluded due to
their specificity to particular cell types or their irrelevance to the construction of our model.
This encompasses a range of effects, including polar interactions~\cite{Duvernoy2018}, extracellular
reactions~\cite{Wang2010} or differentiation processes~\cite{vanGestel2015,Lpez2010}, among numerous
others.
When describing the bacterial system, we distinguish between intra-cellular processes and cell-cell
interactions.
We restrict ourselves to the features discussed below and summarized in
Table~\ref{table:simulation-aspects}.
For a collection of other known aspects which could be considered, we refer to the supplementary
section~\ref{section:discussion}, and~\ref{section:supplement-more-simulation-aspects}.

>>>>

The mechanical behaviour of rod-shaped bacteria is governed by a plethora of effects.
In this work, we aim to establish a model which is general enough such that it can be reused as the
basis for many variants of rod-shaped bacteria but also explicit enough such that we can quantify
its parameters.
We thus utilize only a minimal set of assumptions.

When describing the bacterial system, we distinguish between intra-cellular processes and cell-cell
interactions.
We restrict ourselves to the features discussed below and summarize them in
Table~\ref{table:simulation-aspects}.
% For a collection of other known aspects which could be considered, we refer to the supplementary
% section~\ref{section:discussion}, and~\ref{section:supplement-more-simulation-aspects}.
